Reproducible Research: Peer Assessment 1
==============================================

```{r foo, echo=TRUE}
## Loading and preprocessing the data
activity <- read.csv(".\\activity.csv")
```

## What is mean total number of steps taken per day?
```{r fig.height=10,fig.width=15,echo=TRUE}
stepsum <- tapply(activity$steps,activity$date,sum, na.rm=TRUE)

par(mar = c(6, 4, 2, 1))
barplot(stepsum, main="Total number of steps taken per day", las=2, col="blue")
```

### The mean of total number of steps taken per day
```{r}
stepavg <- tapply(activity$steps,activity$date,mean, na.rm=TRUE)
df <- data.frame(Date=names(stepavg),Avg=stepavg)
print(df,row.names=FALSE)
```

### The median of total number of steps taken per day
```{r}
stepmedian <- tapply(activity$steps,activity$date,median,na.rm = FALSE)
dfmedian <- data.frame(Date=names(stepmedian),Median=stepmedian)
print(dfmedian,row.names=FALSE)
```

## What is the average daily activity pattern?
```{r fig.height=10,fig.width=10,echo=TRUE}

par(pch=22, col="blue")
par(mar = c(6, 4, 2, 1))
plot(as.Date(df$Date,'%Y-%m-%d'), df$Avg, ylab= "average number of steps", type='l', col='blue', xaxt='n', ann=FALSE) 

```

### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
maxdf <- max(df$Avg, na.rm=TRUE)
maxstep <- subset(df, df$Avg == maxdf)
print(maxstep[1][1],row.names=FALSE)
```


## Imputing missing values
### The total number of missing values in the dataset
```{r}
sum(is.na(activity$steps))
```

### Filling all missing value with the mean for that day
```{r fig.height=10,fig.width=15,echo=TRUE}
intervalmean <- mean(activity$steps,na.rm=TRUE)
newactivity <- activity
for(i in 1:length(newactivity$steps)){
  if(is.na(newactivity[i,1])){
    newactivity[i,1] <- intervalmean
  }
}

newstepsum <- tapply(newactivity$steps,newactivity$date,sum, na.rm=TRUE)

par(mar = c(6, 4, 2, 1))
barplot(newstepsum, main="Total number of steps taken per day", las=2, col="blue")
```

### The mean of total number of steps taken per day
```{r}
newstepavg <- tapply(newactivity$steps,newactivity$date,mean, na.rm=TRUE)
newdf <- data.frame(Date=names(newstepavg),Avg=newstepavg)
print(newdf,row.names=FALSE)
```

### The median of total number of steps taken per day
```{r}
newstepmedian <- tapply(newactivity$steps,newactivity$date,median,na.rm = FALSE)
newdfmedian <- data.frame(Date=names(newstepmedian),Median=newstepmedian)
print(newdfmedian,row.names=FALSE)

#### The median value is different from the first part of the assignment.
```

## Are there differences in activity patterns between weekdays and weekends?
```{r fig.height=10,fig.width=10,echo=TRUE}
Sys.setlocale("LC_TIME","English")
newdata <- newactivity
newdata["weekday"] <- weekdays(as.Date(newdata[,2]))
weekday <- subset(newdata,newdata$weekday %in% c('Monday','Tuesday','Wednesday','Thursday','Friday'), select=c(steps,date))
weekend <- subset(newdata,newdata$weekday %in% c('Saturday','Sunday'), select=c(steps,date))

weekdayavg <- tapply(weekday$steps,weekday$date,mean, na.rm=TRUE)
dfweekday <- data.frame(Date=names(weekdayavg),Avg=weekdayavg)

weekendavg <- tapply(weekend$steps,weekend$date,mean, na.rm=TRUE)
dfweekend <- data.frame(Date=names(weekendavg),Avg=weekendavg)

par(pch=22, col="blue")
par(mar = c(6, 4, 2, 1), mfrow = c(2,1))

plot(as.Date(dfweekend$Date,'%Y-%m-%d'), dfweekend$Avg, ylab= "average number of steps", type='l', col='blue', xaxt='n', xlab="interval", main="Weekend")

plot(as.Date(dfweekday$Date,'%Y-%m-%d'), dfweekday$Avg, ylab= "average number of steps", type='l', col='blue', xlab="interval", xaxt='n', main="Weekday") 


```
